Constructive Solid Geometry for Interactive Environments

### 2018-04-04 Paper.tex
Explained OpenGL in paper

In total, seven objects were created using OpenSCAD. These include, but are not limited to, a die, a taurus, an asteroid, a spaceship, and an abstract cookie-cutter.
\subsubsection{OpenGL Implementation}
Once the .stl file is parsed, the vector of \texttt{Facet}s is fed into OpenGL's \texttt{GL{\bf\_}TRIANGLES} primitive to rebuild the object in a more interactive environment. The display program 
\subsection{Asteroids}
\section{Conclusion}
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Appendix}
\subsection{stlReader.cpp}
\lstinputlisting[language=C++]{stlReader.cpp}
\subsection{display.cpp}
\lstinputlisting[language=C++]{display.cpp}
\newpage
\begin{thebibliography}{10}
\bibitem{cs_dictionary}
  Butterfield, Andrew and Gerard Ngondi,
  \textit{A Dictionary of Computer Science},
  Oxford University Press,
  7th edition,
  2016

>>>>

In total, seven objects were created using OpenSCAD. These include, but are not limited to: a die, a torus, an asteroid, a spaceship, and an abstract cookie-cutter.
\subsubsection{OpenGL Implementation}
Once the .stl file is parsed, the vector of \texttt{Facet}s is fed into OpenGL's \texttt{GL{\bf\_}TRIANGLES} primitive to rebuild the object in a more interactive environment. The display program uses a white specular point light and a material shininess of 50. A \texttt{mouse} and \texttt{motion} function enable the user to rotate the object on its axis, with the rotations being performed within the \texttt{display} function. Within the \texttt{glBegin} and \texttt{glEnd} block, the vector \texttt{newShape} is scanned, with each \texttt{Facet}'s normal vector and vertices passed to the respective OpenGL command. In order to correctly light the objects, the vertices are passed in the reverse order they were printed in the .stl file.
\subsection{Asteroids}
\section{Conclusion}
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Appendix}
\subsection{OpenSCAD}
\subsubsection{die.scad}
\subsubsection{connector.scad}
\subsubsection{torus.scad}
\subsubsection{asteroid.scad}
\subsection{C++}
\subsubsection{stlReader.cpp}
%\lstinputlisting[language=C++]{stlReader.cpp}
\subsubsection{display.cpp}
%\lstinputlisting[language=C++]{display.cpp}
\newpage
\begin{thebibliography}{10}
\bibitem{cs_dictionary}
  Butterfield, Andrew and Gerard Ngondi,
  \textit{A Dictionary of Computer Science},
  Oxford University Press,
  7th edition,
  2016
